\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subfigure}
\lstset{ %
language=C++,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
backgroundcolor=\color{white!3!white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)},          % if you want to add a comment within your code
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{green!40!black},
  commentstyle=\itshape\color{gray!80!black},
  identifierstyle=\color{black},
}


\title{\textbf{Project Management Document\\ Parametrized String Matching Implementation for Software Plagiarism Check}}

\author{
		\vspace{ 2 mm}\\
		Supervised By : \textbf{Prof. Srinivasaraghavan G}\\
		\vspace {2mm}\\
		\textbf{Team} \\	
		amit.tomar \\
		(MT2013008) \\
		\vspace{ -1 mm}\\		
		siddhesh.dosi\\								     
		(MT2013150) \\		
		\vspace{ -1 mm}\\					
		srinivas.r.vaidya\\
		(MT2013152) \\
		\vspace{ -2 mm}\\		
		\textbf{@iiitb.org}}
		
\date{10 - April - 2014}

\begin{document}
\lstset{language=C} 
\maketitle

\vspace{ 100 mm}

\section{Introduction}

This project aims at developing a Parametrized String Matching Implementation for Software Plagiarism Check, that given a collection of files which contain code in some programming language, will show a set of possible duplications of parts of the code among these. Comparing pieces of software will require discounting comments (optional and language dependent), extra/blank lines and spaces, variable renaming etc. The theory of parametrized string matching will be used to implementat this project. System will have an easy-to-use UI for selecting files/folders and shall report the plagiarism related information (matches found) in the UI in a nice manner.

\section{Project plan}

\begin{enumerate}
  \item \textbf{Activity list}
  \begin{enumerate}
    \item \textbf{Documentation : Requirement Specification} :  \\
    Date of submission : 7 - Feb - 2014 \\ 
    (Already submitted to Prof. Srinivasraghvan)\\
    
    \item \textbf{Literature Survey} : \\
Expected date of completion : 15 - April - 2014 \\ 
Expected time : 45 Hours

\begin{enumerate}
\item \textbf{Reading relevant background information} : 15 Hours
\item \textbf{Understanding and documenting the requirements} : 15 Hours
\item \textbf{Discussions} : 15 Hours\\
\end{enumerate}

    \item \textbf{Designing a solution : Building suffix tree data structure}:\\
    Expected date of completion : 15 - May - 2014 \\ 
    Expected time : 30 Hours\\
    \item \textbf{Coding : Identifying duplicate code using suffix tree}: \\
    Expected date of completion : 1 - June - 2014 \\ 
    Expected time : 25 Hours\\
    \item \textbf{Coding : Implementation of UI}: \\
    Expected date of completion : 10 - June - 2014 \\ 
    Expected time : 10 Hours\\
    \item \textbf{Coding : Parameterized implementation for software plagiarism check}:\\
    Expected date of completion : 1 - July - 2014 \\ 
    Expected time : 40 Hours\\
    \item \textbf{Integration : UI with parameterized string matching code}:\\
    Expected date of completion : 15 - July - 2014 \\ 
    Expected time : 20 Hours\\
    \item \textbf{Testing}:\\
    Expected date of completion : 31 - July - 2014 \\ 
    Expected time : 20 Hours\\
           
  \end{enumerate}
  \item \textbf{List of final deliverables}:
    \begin{enumerate}
  \item Requirement specification document.
  \item Design document.
  \item User manual.
  \item Deployment manual.
    \end{enumerate}

\end{enumerate}

\section{ Testing Strategy}

  \begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
    
    \textbf{TestCase} & Populate the folder structure of file system. \\ \hline
    \textbf{Input}      & File option \\ \hline
    \textbf{Output}     & User prompted to select files from multiple folder. \\ \hline
        \textbf{Responsibility}     & Amit Tomar  \\ \hline
    
    \end{tabular}
\end{center}

  \begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
     \textbf{TestCase} & File path validation \\ \hline
    \textbf{Input}      & Browsing and selection of files and next button \\ \hline
    \textbf{Output}     & User is promted to enter code snippet to be ignored while processing \\ \hline
    \textbf{Responsibility}     & Amit Tomar  \\ \hline
   
    \end{tabular}
\end{center}

  \begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
     \textbf{TestCase} & Generate parameterized suffix tree to check amount of plagiarism. \\ \hline
    \textbf{Input}      & Check plagiarism \\ \hline
    \textbf{Output}     & Plagiarism related log is generated.  \\ \hline
        \textbf{Responsibility}     & Siddhesh Dosi  \\ \hline
   
    \end{tabular}
\end{center}

  \begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
    \textbf{TestCase} & Search for all the files in the selected folder and populate a list. \\ \hline
    \textbf{Input}      & Folder option \\ \hline
    \textbf{Output}     & User is prompted to select Folder. \\ \hline
   \textbf{Responsibility}     & Siddhesh Dosi  \\ \hline

    
    \end{tabular}
\end{center}

  \begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
    \textbf{TestCase} & File path validation \\ \hline
    \textbf{Input}      & Selection/Deselection of files from the populates list and next button \\ \hline
    \textbf{Output}     & User is promted to enter code snippet to be ignored while processing \\ \hline
    \textbf{Responsibility}     & Srinivas Vaidya  \\ \hline

    
    \end{tabular}
\end{center}

  \begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
    \textbf{TestCase} & Generate parameterized suffix tree to check amount of plagiarism. \\ \hline
    \textbf{Input}      & Check plagiarism \\ \hline
    \textbf{Output}     & Plagiarism related log is generated.  \\ \hline
    \textbf{Responsibility}     & Srinivas Vaidya  \\ \hline
    \end{tabular}
\end{center}                    

\section{Goals of implementation}

Plagiarism is a serious issue in computer
science courses involving assessment of programming
assignments [1]. Being electronic in nature, it is very easy to copy code and it is difficult to differentiate between the original and copied work. Thus, there is a need for a tool to detect plagiarism 
automatically, assisting professor to check for any kind of copying done by students.

\end{document}

